[dcpo_demsupport]

### 2020-10-27 paper/dcpo_demsupport.Rmd
split off appendix

df_plot <- df_result_clsAPSR[[2]] %>% 
  mutate(model = "Claassen 2020")

@@

@@

\newpage
# APPENDIX A: Tabular Results

# Table A1. Democratic Support on Democratic Institutions{#AJPSreplication}
<!-- ## Models of Effect of Democratic Support on Institutional Democratization {#replicateAJPS} -->

```{r tableAJPS, eval=TRUE}
df_tableAJPS %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 8, border = officer::fp_border()) %>% 
  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n))) %>% 
  autofit() 
```

# Table A2. Democratic Institutions on Democratic Support{#APSRreplication}

```{r table APSR, eval=TRUE}
df_tableAPSR %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 8, border = officer::fp_border()) %>% 
  autofit()

>>>>

df_plot <- df_result_clsAPSR[[2]] %>% 
  mutate(model = "Claassen 2020b")

@@

```{r save_tables, eval=TRUE}
save(df_tableAJPS, df_tableAPSR, file = here::here("output", "df_tables.rda"))

@@

# References

<div id="refs"></div>
